Water Management

### 2020-02-24 Paper/paper.tex
forward simulation

\subsubsection{TODO: Forward Simulation}

% Finally, we want to compute the value of the steady state by using a monte carlo simulation.

>>>>

\subsubsection{Forward Simulation}
In order to simulate the problem, we developed a so called forward simulation which is run once for each period to be simulated.
It consists of several steps that will be described in more detail here.
At the begin of each period the code determines how much water according to the irrigation policy to be used for irrigation.
Since the simulation starts with an empty reservoir the amount irrigated in the first period is zero.
Then the water level for the next iteration is calculated.
This calculation is based on the irrigation amount, the current water level, the amount of rain and the amount that went away by evaporation (see \ref{sec:intro-mod4}).
Afterwards the simulation calculates the difference in water level of the period compared to its predecessor, which will be used for finding a steady state.
% Finally, we want to compute the value of the steady state by using a monte carlo simulation.
